### 2021-03-31 input/proposal.tex
wip

\begin{definition}[\underline{S}coped broadcast (S-broadcast)]
  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct Process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
  processes, \underline{m}etadata $\mu$ within received messages, and
  a \underline{p}redicate $\phi$ verified from process to process:
  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
\end{definition}

This definition highlights the transitive relevance of messages and
encompasses more specific definitions of related
work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
process from Paris could scoped broadcast a message to all processes
in this city. A process from Paris could scoped broadcast a message to
all processes in this city plus neighboring cities by overloading
forwarded messages the first time they reach another city. Similarly
to reliable broadcast, scoped broadcast implementations expose
different trade-offs on space, time, and communication.

@@

In this paper, we propose to dynamically adapt the scope of
S-broadcast using S-broadcast itself. At any time, a process can
become the source of a new logical partition by transitively modifying
the respective state of neighboring processes using path weights. When
a process S-broadcasts a message in this partition, it eventually
reaches all processes belonging to this partition.  While the first
partition gathers all processes of the system, the following
partitions reduce the membership size of their neighboring
partitions. In turns, the traffic generated to adapt scopes scales
with the number of partitions.

@@

In this section, we introduce \NAME (stands for \underline{A}daptive
\underline{S}coped broad\underline{cast}), a wait-free reactive
protocol for dynamic logical partitioning in dynamic distributed
systems the cost of which actually depends on its usage. At any time,
processes can add \emph{and} remove partitions from the system. When
the system becomes quiescent, processes eventually converge to their
respective partition and do not require further communication
afterward.

Each process works autonomously and asynchronously, in a peer-to-peer
fashion. Each process broadcasts each change to its neighborhood, for
the state of its neighbors may depend on this change as well. Yet, the
traffic generated to to adapt the scope of scoped broadcast remains
bounded, for it uses the principles of scoped broadcast
itself. Messages that carry changes travel through the network
depending on partition of processes, stopping as soon as they
encounter uninterested processes. We demonstrate that \NAME guarantees
consistent partitioning despite different order in message deliveries
from one process to another.

%% This section starts by describing \NAME's functioning by detailing its
%% operation to avoid inconsistent states due to ordering and staleness
%% of delivered messages. This section ends with a complexity analysis of
%% proposed protocols.

%% \subsection{Intra-autonomous system partitioning}

@@

%% In this section, we aim at solving Problem Statement~\ref{prob:intra}
%% by proposing \NAME, a reactive logical partitioning protocol for
%% dynamic partitioning in dynamic networks.

\subsection{Principle}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:scoped}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

@@

\noindent Each process must also maintain the partition it belongs to,
along with its control informations. Among other, it must maintain a
path the size of which depends on the membership size of the
partition. In the worst case, this path includes the identity of every
process of the system that currently belong to the system. Eventually,
the size of this path increases linearly with the diameter of the
current partition. \TODO{assuming weight equals 1 \ldots}

>>>>

\begin{definition}[\underline{S}coped broad\underline{cast} (\NAMEB)]
  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct Process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
  processes, \underline{m}etadata $\mu$ within received messages, and
  a \underline{p}redicate $\phi$ verified from process to process:
  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
\end{definition}

This definition highlights the transitive relevance of messages and
encompasses more specific definitions of related
work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
process from Paris could scoped broadcast a message to all processes
in this city. A process from Paris could scoped broadcast a message to
all processes in this city plus neighboring cities by overloading
forwarded messages the first time they reach another city. Similarly
to reliable broadcast, scoped broadcast implementations expose
different trade-offs on space, time, and communication. In this paper,
we introduce an adaptive scoped broadcast the cost of which actually
depends on its operations, and the current scopes that exist in the
system.

@@

In this section, we propose to dynamically adapt the scopes of \NAMEB
using \NAMEB itself for the sake of efficiency. At any time, a process
decides whether or not it becomes the center (or \emph{source}) of a
scope (or \emph{partition}). Processes must eventually rally the
partition corresponding to their closest source despite concurrent
operations, and dynamic changes in the network.

\noindent In that regard, we introduce \NAME (stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}), a
wait-free reactive protocol for dynamic logical partitioning that
enables adaptive scoped broadcast in dynamic distributed
systems. \NAME's operation guarantees that processes eventually reach
consistent partitioning by efficiently propagating their state
changes. \NAME's overhead actually depends on its operations and
current partitions in the system. In other terms,
\begin{inparaenum}[(i)]
\item when the system becomes quiescent, processes eventually converge to
their respective partition and do not require further communication
afterward; and
\item processes do not pay the price of past partitioning.
\end{inparaenum}

\noindent This section starts by introducing consistent partitioning
and its implementation when a process can only become a new source to
create a new partition, i.e., it cannot revoke its self-appointed
status of source. Then, it extends to include the latter behavior: it
introduces the properties that guarantee consistent partitioning in
such context, and it details our implementation called \NAME. Finally,
it provides the complexity analysis of \NAME divided in time, space,
and communication.

\subsection{Consistent partitioning}

At any time, a process can decide to become a source. \TODO{more.}

@@

@@

\subsection{Dynamic consistent partitioning}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:scoped}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

@@

\noindent Each process must also maintain the partition it belongs to,
along with its control information. Among other, it must maintain a
path the size of which depends on the membership size of the
partition. In the worst case, this path includes the identity of every
process of the system that currently belong to the system. Eventually,
the size of this path increases linearly with the diameter of the
current partition. \TODO{assuming weight equals 1 \ldots}
